---
title: "week-5"
author: "Nikita Krähenbühl"
date: "5/13/2022"
output: html_document
---
```{r setup, include=FALSE}
library(readr)
library(tidyverse)
library(sf)
library(terra)
library(dplyr)
library(lubridate)
library(ggplot2)
library(tmap)
library(rayshader)
library(RColorBrewer)
```

# Task 1: Read Data

```{r}
wildschwein_BE <- read_delim("rawdata/wildschwein_BE_2056.csv",",") %>%
  st_as_sf(coords = c("E", "N"), crs = 2056, remove = FALSE)

fanel <- read_sf("rawdata/Feldaufnahmen_Fanel.gpkg")

str(fanel)
summary(fanel)

plot(fanel)
```
What information does the dataset contain? Fields with vegetation types
What is the geometry type of the dataset (possible types are: Point, Lines and Polygons)? Polygon
What are the data types of the other columns? Character and Integer
What is the coordinate system of the dataset? LV95


# Task 2: Annotate Trajectories
Filter to summer
```{r}
wildschwein_BE %>% 
  filter(DatetimeUTC >= as.Date("2015-05-01") & DatetimeUTC < as.Date("2015-07-01")) -> ws_summer

ggplot() +
  geom_sf(data= fanel, aes(fill = Frucht)) +
  geom_sf(data = ws_summer) + theme_void()

st_join(ws_summer, fanel) %>%
  mutate(round_DatetimeUTC = round_date(DatetimeUTC, unit = "hours"),
         hours = format(round_DatetimeUTC, "%H"))-> ws_annotate

```

# Task 3: Explore the annotated dataset
```{r}
ws_annotate %>% 
  group_by(Frucht, TierName) %>% 
  summarise(minTime = min(round_DatetimeUTC), maxTime = max(round_DatetimeUTC), n=n()) %>% 
  mutate(duration = as.numeric(difftime(maxTime, minTime, units="hours"))) %>% 
  ggplot(.) + geom_bar(aes(x = hours, fill = Frucht))

ws_annotate %>% 
  group_by(Frucht, TierName) %>% 
  mutate(duration = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC), units="hours")) -> t

ws_annotate %>% 
  ggplot(.) + geom_bar(aes(x = hours, fill = Frucht),
                       position = "fill") + theme_classic() + facet_wrap(~TierName) + coord_polar()

```

# Task 4: Raster Data
```{r}
library(tmap)
terra::rast("rawdata/vegetationshoehe_LFI.tif") -> vegetation

```

# Task 5: Extract Data from Raster
```{r}
terra::extract(vegetation, vect(wildschwein_BE)) %>% 
  cbind(wildschwein_BE, .) %>% 
  st_as_sf(.) -> wildschwein_BE


wildschwein_BE %>% select(geometry, vegetationshoehe_LFI) %>% 
ggplot() +
  geom_sf(data = wildschwein_BE, aes(color = vegetationshoehe_LFI)) -> gg
gg
plot_gg(gg)


ggplot() +
  geom_point(data=wildschwein_BE, aes(x=E, y = N, color = vegetationshoehe_LFI)) + coord_fixed() -> gg1
plot_gg(gg1)
```

